\documentclass{muratcan_cv}

\setname{Magu Raam Prasaad}{R}
\setaddress{Bengaluru/India}
\setmobile{+91 9791521360}
\setmail{maguprasaad@iisc.ac.in}
\setposition{PhD student} %ignored for now
 %you can play with color of the template (red is also nice..)
\setbitbucketaccount{https://bitbucket.org/MaguRaam/} %you can play with color of the template (red is also nice..)
\setthemecolor{red} %you can play with color of the template (red is also nice..)

\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
% Summary
\addblocktext{Summary}{
    I am a Ph.D. student in the Indian Institute of Science Mechanical Department. I work on large-scale numerical simulation of single and multiple cavitation bubble collapse process to develop a detailed understanding of acoustic wave emission and propagation. Broadly my research interests are in numerical simulation of partial differential equations and high-performance computing to solve complex multiphysics problems.
}
%
%Education
\section{Education} 
    \datedexperience{Shiv Nadar University}{2013-2017} 
    \explanation{BTech in Mechanical Engineering and Minor in Physics} 
    \datedexperience{Shiv Nadar University}{2017-2019} 
    \explanation{MTech in Mechanical Design} 
%Experience
\section{Experience}
%
    \datedexperience{Research Assistant}{2019-Summer / SNU} 
    \explanation{Research Assitant in Naval Research Board project} 
%

%
% Research Project
\section{Research Projects}
    %
    \datedexperience{Master’s Thesis}{  2018-2019/ SNU} 
    \explanationdetail{OpenFOAM implementation of Immersed Boundary Method for fluid-structure interaction.} 
    \datedexperience{Naval Research Board project}{  2019-Summer/ SNU}
    \explanationdetail{Numerical Simulation of Manta Ray propulsion using Immersed Boundary Method to develop under water vehicle.}
    \datedexperience{PhD Project}{2019-current/ IISc} 
    \explanationdetail{
    Large-scale numerical simulation of single and multiple cavitation bubble collapse process to develop a detailed understanding of acoustic wave emission and propagation.
     }
%Conference publication
\section{Conference}
\datedexperience{}{}
\explanationdetail{Magu Raam Prasaad R, Ajit Kumar and Santanu Mitra, “OpenFOAM implementation of immersed boundary method to simulate fluid-solid interaction problems” , ICCM2019, July 9th-13th, Singapore THE 10THINTERNATIONAL CONFERENCE ON COMPUTATIONAL METHODS.}
\datedexperience{}{}\\
\explanationdetail{Magu Raam Prasaad R and Venkatramani J, Investigating the route to flutter in a pitch-plunge airfoil with freeplay nonlinearity subjected to input flow fluctuations,VETOMAC 2018,Lisbon,Portugal,10-13,September-2018.}

\section{Skills}
    %
    \newcommand{\skillone}{\createskill{Programming Languages}{\textbf{\emph{Experienced:}} \ \  C \cpshalf C++ \ \ \textbf{\emph{Familiar:}} Python \cpshalf  Julia }}
    %
    \newcommand{\skilltwo}{\createskill{Parallel Computing}{MPI} and experience in HPC}
    %
    \newcommand{\skillthree}{\createskill{Programming Paradigms}{Object-Oriented Programming \cpshalf Generic Programming \cpshalf Functional Programming}}
    \newcommand{\skillfour}{\createskill{Numerical Libraries}{PETSc \cpshalf deal.II \cpshalf OpenFOAM}}
    %
    \newcommand{\skillfive}{\createskill{Visualization and Meshing Tools}{ParaView \cpshalf VisIt \cpshalf Gmsh}}
    %
    \newcommand{\skillsix}{\createskill{Other Tools and Libraries}{ Git \cpshalf Latex \cpshalf STL \cpshalf Blitz++ \cpshalf Numpy \cpshalf Matplotplib }}
    %

 \newcommand{\skillseven}{\createskill{Languages}{\textbf{\emph{Native:}} \ \  Tamil \ \ \textbf{\emph{Fluent:}} \ \ English  }}
    %
    \createskills{\skillone, \skilltwo, \skillthree, \skillfour, \skillfive, \skillsix, \skillseven}
\section{Hobbies}
    \newcommand{\extraone}{Playing basketball}
    \newcommand{\extratwo}{Long distance-running}
    \newcommand{\listofextras}{\extraone, \extratwo}
    \createbullets{\listofextras}
%Footnote
\createfootnote
\end{document}
